Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)

### 2024-12-03 paper/paper.qmd
initial

[Appendix -@sec-model-details].

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

RMSE measures the square root of the average squared differences between the predicted and observed values. In the context of this model, RMSE quantifies how closely the predicted life expectancy values align with the actual observed values. Lower RMSE values indicate better model performance, suggesting that the model’s predictions are close to the true values.

By calculating RMSE, we can assess the goodness-of-fit of the model, with lower values indicating less error and higher precision in predicting life expectancy. It is particularly useful in comparing different models or iterations to select the best-performing one.

@@

## Overview of model results
Our results are summarized in @tbl-modelresults. We are primarily interest in the

@@

### Idealized Survey

@@

Income Group:
-   Low Income (Less than $1,000/year)
-   Lower-Middle Income (\$1,001 - \$10,000/year)
-   Upper-Middle Income (\$10,001 - \$50,000/year)
-   High Income (More than \$50,000/year)

@@

# Model details {#sec-model-details}

@@

## RMSE table

@@

### Additional graph for analysis

>>>>

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`. More explanation of the model could be found [Appendix -@sec-model-details].

@@

RMSE measures the square root of the average squared differences between the predicted and observed values. In the context of this model, RMSE quantifies how closely the predicted life expectancy values align with the actual observed values. Lower RMSE values indicate better model performance, suggesting that the model’s predictions are close to the true values. The generalizability is checked by comparing rmse_test and rmse_train. Seeing the test RMSE is slightly lower than the training RMSE, the model generalizes well.

@@

## Overview of model results

Our results are summarized in @tbl-modelresults. We are primarily interest in the

@@

## Idealized Survey

@@

Income Group: - Low Income (Less than \$1,000/year) - Lower-Middle Income (\$1,001 - \$10,000/year) - Upper-Middle Income (\$10,001 - \$50,000/year) - High Income (More than \$50,000/year)

@@

## Model details {#sec-model-details}

@@

## RMSE Full table

@@

## Additional graph for analysis
